### 2023-03-16 manuscript.Rmd
Refactor code to source files

```{r, eeg_processing, include=FALSE}
# Define function for processing behavioral log files
read_log <- function(log_file) {
  # Read the file
  log <- read_tsv(
    log_file,
    col_types = cols(),
    locale = locale(encoding = "latin1"),
    progress = FALSE
  ) %>%
    # Recode some columns
    transmute(

      # Phase of the experiment
      phase = factor(
        Wdh,
        levels = c(211, 212, 213),
        labels = c("Pre-insight", "Insight", "Post-insight")
      ),

      # Unfamiliar versus familiar objects
      familiarity = factor(
        bek_unbek,
        levels = c("bekannt", "unbekannt"),
        labels = c("familiar", "unfamiliar")
      ),

      # Matching versus non-matching keywords for unfamiliar objects
      keywords = factor(
        Bed,
        levels = c("richtig", "falsch"),
        labels = c("Match", "Non-match")
      ),

      # Behavioral responses
      # Response code 201: "I know what this is or have a strong assumption"
      # Response code 202: "I have an assumption what this is"
      # Response code 203: "I have rather no assumption what this is"
      # Response code 204: "I don't know what this is and have no assumption"
      # Response code 0: Technical glitch
      response = Tastencode,

      # Reaction times
      rt = RT,

      # Item IDs
      item_id = factor(StimID)
    ) %>%
    # Remove filler items
    filter(familiarity == "unfamiliar")

  # Assign items to conditions based on manipulation (matching vs. non-
  # matching keywords) and the responses of the participants
  items_per_condition <- with(log, {
    list(

      # Informed condition: Matching keywords and positive response
      Informed = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(201, 202)
      ],

      # Uninformed condition: Non-matching keywords and negative response
      Uninformed = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(203, 204)
      ],

      # Exclude: Matching keywords and negative response
      Unsuccessful = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(203, 204)
      ],

      # Exclude: Non-matching keywords and positive response
      Exclude_uninformed = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(201, 202)
      ],

      # Exclude: Positive response *before* any info was presented
      Exclude_known = item_id[phase == "Pre-insight" & response == 201],

      # Exclude: Technical glitch
      Exclude_glitch = item_id[phase == "Insight" & response == 0]
    )
  })

  # Assign these conditions to the trials of all three phases
  log$condition <- NA
  for (condition in names(items_per_condition)) {
    item_id <- items_per_condition[[condition]]
    log$condition[log$item_id %in% item_id] <- condition
  }

  # Sort columns
  log %>%
    select(item_id, phase, condition, response, rt)
}

# Get list of behavioral log files
log_files <- c(
  list.files(here(data_dir, "rt/exp1"), "*.txt", full.names = TRUE),
  list.files(here(data_dir, "rt/exp2"), "*.txt", full.names = TRUE)
)

# Get list of BrainVision EEG header files
vhdr_files <- c(
  list.files(here(data_dir, "eeg/exp1"), "*.vhdr", full.names = TRUE),
  list.files(here(data_dir, "eeg/exp2"), "*.vhdr", full.names = TRUE)
)

# Import EEG pipeline from Python
pipeline <- import("pipeline")

# Extract versions of Python packages
pipeline_version <- pipeline$`__version__`
mne_version <- import("mne")$`__version__`

# (Re-)do the actual preprocessing if requested
if (run$eeg_processing) {
  # Process behavioral data
  logs <- map(log_files, read_log)

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      name = list("P1", "N170", "N400"),
      tmin = list(0.1, 0.15, 0.4),
      tmax = list(0.15, 0.2, 0.7),
      roi = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = list(
      pre_informed =
        "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
      pre_uninformed =
        "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
      pre_unsuccessful =
        "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
      ins_informed =
        "phase == 'Insight' & condition == 'Informed' & rt > 200",
      ins_uninformed =
        "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
      ins_unsuccessful =
        "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
      post_informed =
        "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
      post_uninformed =
        "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
      post_unsuccessful =
        "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
    ),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Uninformed"),
      c("Insight/Informed", "Insight/Uninformed"),
      c("Post-insight/Informed", "Post-insight/Uninformed"),
      c("Insight/Informed", "Insight/Unsuccessful")
    ),
    tfr_components = list(
      name = list("alpha_beta"),
      tmin = list(0.6),
      tmax = list(1.2),
      fmin = list(8.0),
      fmax = list(20.0),
      roi = list(c("P3", "P4", "Pz", "PO3", "PO4", "POz"))
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 4
  )
}

@@

# Compute number of objects per condition for each participant
objects_per_condition <- with(trials, table(participant_id, condition)) %>%
  `/`(3) %>%
  as.data.frame.matrix() %>%
  rownames_to_column("subject_id")

# Read by-participant ERP averages and channel locations
evokeds <- read_csv(here(output_dir, "ave.csv")) %>%
  separate(label, into = c("phase", "condition"), sep = "/")

@@

# Define helper function for fitting linear mixed models and computing contrasts
fit_mixed_models <- function(dep, formula, data) {
  # Modify the formula such that fixed effects are always retained
  formula <- formula %>%
    tabulate.formula() %>%
    mutate(block = replace(block, is.na(grouping), "fixed"))

  # Start a CPU cluster so that multiple models can be fitted in parallel
  n_cores <- detectCores()
  cl <- makeCluster(n_cores)

  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
  build <- buildmer(
    buildmerControl = buildmerControl(
      formula, data,
      args = list(control = lme4::lmerControl(
        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
      )),
      direction = c("backward", "backward"),
      cl = cl,
      elim = LRTalpha(.20),
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  stopCluster(cl)

  # Compute marginal means and contrasts
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  emm_means <- emmeans(build@model, specs = c("phase", "condition"))
  emm_contrasts <- contrast(
    emm_means,
    method = "trt.vs.ctrl", simple = "condition", reverse = TRUE
  ) %>%
    summary(by = "contrast", adjust = "bonferroni")

  # Create list of returns
  list(
    model = build@model,
    summary = build@summary,
    anova = build@anova,
    means = emm_means,
    contrasts = emm_contrasts
  )
}

# (Re-)do the actual model fitting if requested
deps <- config$components$name
if (run$mixed_models) {
  # Fit the model for each ERP component
  form_erps <- ~ phase * condition + cosine +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models <- map(deps, fit_mixed_models, formula = form_erps, data = trials) %>%
    set_names(deps)

  # Fit an additional control analysis model for the alpha/beta power
  form_alpha_beta <- ~ phase * condition + rt + cosine +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models$alpha_beta <- fit_mixed_models(
    dep = "alpha_beta", formula = form_alpha_beta, data = trials
  )

@@

# Extract relevant statistics to print in the main text
anova_table <- models %>%
  map(function(model) as_tibble(model$anova, rownames = "effect")) %>%
  bind_rows(.id = "component") %>%
  rename(f_value = `F value`, p_value = `Pr(>F)`)
contrast_table <- models %>%
  map(function(model) as_tibble(model$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`)
```

@@

The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4)) based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a high-pass filtered copy of the data (cutoff = 1 Hz).
A variable number of components per participant were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (mean = `r mean(unlist(config$auto_ica_n_components))` components, range `r min(unlist(config$auto_ica_n_components))`--`r max(unlist(config$auto_ica_n_components))`).
Then the ICA was fitted based on these components using the FastICA algorithm [@hyvarinen1999].
Any independent components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using MNE-Python's *find_bads_eog* method.
This was the case for an average of `r mean(lengths(config$auto_ica_bad_components))` components per participant (range = `r min(lengths(config$auto_ica_bad_components))`--`r max(lengths(config$auto_ica_bad_components))` components).

@@

```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:fig4-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed"
  ),
  p_cluster = p_cluster
)
```

@@

```{r tabs1, results="asis"}
# Print table of materials
keywords %>%
  filter(familiarity == "unfamiliar") %>%
  transmute(
    img = paste0(
      "\\includegraphics[valign=c,width=18mm]{materials/unfamiliar_objects/",
      filename,
      "}"
    ),
    item_id = as.character(item_id),
    match_translated = paste(match, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch_translated = paste(nonmatch, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c(
      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
    ),
    escape = FALSE,
    longtable = TRUE,
    caption = "Unfamiliar Object Stimuli\\smallskip",
    font_size = "footnotesize"
  )
```

@@

```{r, ress1a}
# Helper function for printing model summary, ANOVA (F tests), and contrasts
print_model_outputs <- function(model_object) {
  model_object$summary$call$data <- NULL # Prevents cluttering the output
  print(model_object$summary)
  cat("\n")
  print(model_object$anova)
  cat("\nPairwise Contrasts (Simple Effects)\n")
  print(model_object$contrasts)
  cat("\n\n")
}

# Print model outputs
print_model_outputs(models$P1)
```

@@

```{r, ress1b}
# Print model outputs
print_model_outputs(models$N170)
```

@@

```{r, ress1c}
# Print model outputs
print_model_outputs(models$N400)
```

@@

```{r, figs1, cache=FALSE, fig.height=5, fig.width=6, out.width="50%", fig.cap="(ref:figs1-caption)"}
rating %>%
  filter(!is.na(cosine)) %>%
  mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
  ggplot(aes(x = condition_comb, y = cosine, color = condition_comb)) +
  geom_violin(fill = NA) +
  geom_boxplot(width = 0.2) +
  scale_y_continuous(limits = c(0.0, 1.0), breaks = seq(0.0, 1.0, by = 0.2)) +
  scale_color_manual(values = c("#5e3c99", "#ca0020", "#0571b0")) +
  labs(x = NULL, y = "Cosine distance to keywords") +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_classic() +
  theme(
    axis.title = element_text(color = "black", size = 10.9),
    axis.text = element_text(color = "black", size = 10.9),
    legend.position = "none",
    panel.grid.major.y = element_line(),
    panel.grid.minor.y = element_line()
  )
```

@@

```{r, figs2, cache=FALSE, fig.height=5.5, fig.cap="(ref:figs2-caption)"}
rating %>%
  filter(!is.na(cosine) & condition == "matching") %>%
  mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
  select(item_id, condition_comb, cosine) %>%
  group_by(item_id, condition_comb) %>%
  summarize(
    mean = mean(cosine),
    sd = sd(cosine),
    n = n(),
    se = sd / sqrt(n),
    .groups = "drop"
  ) %>%
  mutate(item_id = fct_reorder(item_id, desc(mean))) %>%
  ggplot(
    aes(
      x = item_id, y = mean, color = condition_comb, group = 1,
      ymin = mean - se, ymax = mean + se
    )
  ) +
  geom_linerange(show.legend = FALSE) +
  geom_line() +
  labs(x = "Stimulus ID", y = "Cosine distance to keywords", color = NULL) +
  scale_x_discrete(guide = guide_axis(angle = 90, n.dodge = 3)) +
  scale_y_continuous(limits = c(0.0, 1.0), breaks = seq(0.0, 1.0, by = 0.2)) +
  scale_color_manual(values = c("#5e3c99", "#ca0020")) +
  theme_classic() +
  theme(
    axis.title = element_text(color = "black", size = 10.9),
    axis.text = element_text(color = "black", size = 10.9),
    legend.position = c(0.93, 0.92),
    panel.grid.major.x = element_line(),
    panel.grid.major.y = element_line(),
    panel.grid.minor.y = element_line()
  )
```

@@

```{r, figs3, cache=!run$figures, fig.height=11, fig.cap="(ref:figs3-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(
    tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed"
  ),
  p_cluster = p_cluster
)
```

@@

```{r, figs4, cache=!run$figures, fig.height=11, fig.cap="(ref:figs4-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(
    tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful"
  ),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

@@

```{r, figs5, cache=!run$figures, fig.height=11, fig.cap="(ref:figs5-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful"
  ),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

@@

```{r, figs6, cache=!run$figures, fig.height=11, fig.cap="(ref:figs6-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters,
    contrast == "Post-insight/Informed - Post-insight/Unsuccessful"
  ),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

>>>>

```{r, eeg_processing, include=FALSE}
# (Re-)do the EEG preprocessing if requested
if (run$eeg_processing) {
  # List behavioral log files and raw EEG files
  log_files <- c(
    list.files(here(data_dir, "rt/exp1"), "*.txt", full.names = TRUE),
    list.files(here(data_dir, "rt/exp2"), "*.txt", full.names = TRUE)
  )
  vhdr_files <- c(
    list.files(here(data_dir, "eeg/exp1"), "*.vhdr", full.names = TRUE),
    list.files(here(data_dir, "eeg/exp2"), "*.vhdr", full.names = TRUE)
  )

  # Process behavioral data
  logs <- map(log_files, read_log)

  # Process EEG data
  pipeline <- import("pipeline")
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      name = list("P1", "N170", "N400"),
      tmin = list(0.1, 0.15, 0.4),
      tmax = list(0.15, 0.2, 0.7),
      roi = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = list(
      `Pre-insight/Informed` =
        "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
      `Pre-insight/Uninformed` =
        "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
      `Pre-insight/Unsuccessful` =
        "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
      `Insight/Informed` =
        "phase == 'Insight' & condition == 'Informed' & rt > 200",
      `Insight/Uninformed` =
        "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
      `Insight/Unsuccessful` =
        "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
      `Post-insight/Informed` =
        "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
      `Post-insight/Uninformed` =
        "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
      `Post-insight/Unsuccessful` =
        "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
    ),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Uninformed"),
      c("Pre-insight/Informed", "Pre-insight/Unsuccessful"),
      c("Insight/Informed", "Insight/Uninformed"),
      c("Insight/Informed", "Insight/Unsuccessful"),
      c("Post-insight/Informed", "Post-insight/Uninformed"),
      c("Post-insight/Informed", "Post-insight/Unsuccessful")
    ),
    tfr_components = list(
      name = list("alpha_beta"),
      tmin = list(0.6),
      tmax = list(1.2),
      fmin = list(8.0),
      fmax = list(20.0),
      roi = list(c("P3", "P4", "Pz", "PO3", "PO4", "POz"))
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 8
  )
}

@@

# Compute number of objects per condition for each participant
objects_per_condition <- table(trials$participant_id, trials$condition) %>%
  `/`(3) %>% # Each object is shown three times
  as.data.frame.matrix() %>%
  rownames_to_column("subject_id")

# Read by-participant ERP averages
evokeds <- read_csv(here(output_dir, "ave.csv")) %>%
  separate(label, into = c("phase", "condition"), sep = "/")

@@

# (Re-)fit linear mixed models if requested
if (run$mixed_models) {
  # Fit the model for each ERP component
  deps <- config$components$name
  formula_erps <- ~ phase * condition + cosine +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models <- map(deps, fit_mixed_model, formula_erps, trials) %>%
    set_names(deps)

  # Fit an additional control analysis model for the alpha/beta power
  formula_tfr <- ~ phase * condition + rt + cosine +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models$alpha_beta <- fit_mixed_model("alpha_beta", formula_tfr, trials)

@@

# Extract relevant statistics to print in the main text
anova_table <- extract_anova_table(models)
contrast_table <- extract_contrast_table(models)
```

@@

The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4)) based on the MNE-Python software [Version `r config$package_versions$mne`\; @gramfort2013] in Python [Version `r config$package_versions$python`\; @vanrossum2009].
First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a high-pass filtered copy of the data (cutoff = 1 Hz).
A variable number of components per participant were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (mean = `r mean(unlist(config$auto_ica_n_components))` components, range `r min(unlist(config$auto_ica_n_components))`--`r max(unlist(config$auto_ica_n_components))`).
Then the ICA was fitted based on these components using the FastICA algorithm [@hyvarinen1999].
Any independent components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using MNE-Python's *find_bads_eog* method.
This was the case for an average of `r mean(lengths(config$auto_ica_bad_components))` components per participant (range = `r min(lengths(config$auto_ica_bad_components))`--`r max(lengths(config$auto_ica_bad_components))` components).

@@

```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:fig4-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed"),
  p_cluster = p_cluster
)
```

@@

```{r tabs1, results="asis"}
# Print table of materials
print_materials_table(keywords)
```

@@

```{r, ress1a}
# Print model outputs for P1
print_model_outputs(models$P1)
```

@@

```{r, ress1b}
# Print model outputs for N170
print_model_outputs(models$N170)
```

@@

```{r, ress1c}
# Print model outputs for N400
print_model_outputs(models$N400)
```

@@

```{r, figs1, cache=FALSE, fig.height=5, fig.width=6, out.width="50%", fig.cap="(ref:figs1-caption)"}
# Plot rating study results
plot_figs1(rating)
```

@@

```{r, figs2, cache=FALSE, fig.height=5.5, fig.cap="(ref:figs2-caption)"}
# Plot rating study result on the item level
plot_figs2(rating)
```

@@

```{r, figs3, cache=!run$figures, fig.height=11, fig.cap="(ref:figs3-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed"),
  p_cluster = p_cluster
)
```

@@

```{r, figs4, cache=!run$figures, fig.height=11, fig.cap="(ref:figs4-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful"),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

@@

```{r, figs5, cache=!run$figures, fig.height=11, fig.cap="(ref:figs5-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful"),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

@@

```{r, figs6, cache=!run$figures, fig.height=11, fig.cap="(ref:figs6-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Unsuccessful"),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```
